### Assay & Phenotype Intelligence
- 1.0 [x] **Hydrophobicity / HIC Risk Mapping** — investigate how hydrophobic interaction chromatography reflects biophysical liabilities in GDPa1.
  - 1.1 [x] Literature review: salt-mediated retention mechanics and Kyte–Doolittle modulation patterns.
  - 1.2 [x] Evidence scan: CDR-H3 aromatic cluster signatures tied to aggregation alerts.
  - 1.3 [x] Analysis brief: structure-lite (IgFold) contact proxies vs. observed HIC variance.
- 2.0 [x] **Polyreactivity / PSP Signatures** — study CHO lysate binding determinants and entropy-linked polyspecificity risks.
  - 2.1 [x] Threshold mapping: VH/VL charge imbalance and PR_CHO excursions.
  - 2.2 [/] Motif atlas: basic residue run-length patterns triggering QA escalations.
    - 2.3 [/] Entropy study: polyspecificity risk stratification across surprisal tiers.
- 3.0 [x] **Self-Association Nano-Assays** — examine AC-SINS pH 7.4 nanoparticle behavior and related colloidal metrics.
  - 3.1 [x] Mechanistic survey: aromatic exposure, hydrophobic patches, and colloidal shifts.
  - 3.2 [x] Modeling note: incorporating Markov surprisal tiers into self-association scoring.
  - 3.3 [x] Cross-assay comparison: AC-SINS pH 6.0 and DLS-kD concordance checks.
- 4.0 [x] **Thermostability / Fab Transition Metrics** — characterize nanoDSF-derived Tm2 dynamics and structure-aware correlates.
  - 4.1 [x] Structural correlation: hydrogen-bond density, β-sheet propensity, loop RMSD vs. Tm2.
  - 4.2 [x] QA baseline: nanoDSF vs. DSF agreement in GDPa1 reporting.
  - 4.3 [x] Subclass analysis: isotype-driven shifts in thermostability outcomes.
- 5.0 [/] **Expression Yield / Manufacturability** — explore sequence and process levers shaping Valita titer outputs.
  - 5.1 [ ] Glycosylation study: motif abundance vs. yield performance.
  - 5.2 [ ] Charge balance memo: surface charge, surprisal curriculum, and titer trends.
  - 5.3 [ ] Process context: cell line and purification factors influencing yield metrics.

### Data Integrity & Pipeline Control
- 6.0 [ ] **Bioinformatics Intake & Fold Integrity** — research best practices for GDPa1 preprocessing discipline and leakage prevention.
  - 6.1 [ ] Audit methods: ANARCI numbering fidelity and VH/VL pairing verification techniques.
  - 6.2 [ ] Governance review: fold stewardship, leakage audits, and documentation standards.
  - 6.3 [ ] Provenance survey: hash manifest strategies, dataset immutability enforcement, incident escalation playbooks.

### Feature Stack & Modeling Systems
- 7.0 [ ] **Statistical Features & Surprisal Curriculum** — refine knowledge of Markov modeling, smoothing, and entropy-aware training schedules.
  - 7.1 [ ] Benchmark dossier: k-mer (2–5) surprisal statistics with varied smoothing.
  - 7.2 [ ] Curriculum blueprint: surprisal bucket thresholds and unlock heuristics.
  - 7.3 [ ] Coupling study: heavy/light mutual information informing gating decisions.
- 8.0 [ ] **Pattern-Based Test (PBT) Arsenal** — catalog deterministic heuristics supporting QA and explanatory signals.
  - 8.1 [ ] Detector library: sliding-window hydrophobic hotspot methodologies.
  - 8.2 [ ] Motif intelligence: trie-based alerts surfacing structural liabilities.
  - 8.3 [ ] Alignment brief: dynamic-program scoring as anomaly indicators.
- 9.0 [ ] **Protein LM & Embedding Strategies** — consolidate usage patterns and reproducibility guidance for antibody LMs.
  - 9.1 [ ] Comparative review: p-IgGen, ESM-2, AntiBERTa, AbLang embeddings on GDPa1.
  - 9.2 [ ] Provenance protocol: tokenizer/model hashing and throughput budgeting practices.
  - 9.3 [ ] Adapter vs. probe case studies across developability targets.
- 10.0 [ ] **Heavy–Light Coupling & Isotype Systematics** — analyze paired-chain interactions and subclass-dependent effects.
  - 10.1 [ ] Mutual-information profiling: CDRH3/CDRL3 co-motif trends.
  - 10.2 [ ] Subclass dossier: isotype-linked assay deviations and modeling adjustments.
  - 10.3 [ ] Feature integration note: coupling descriptors in ensemble membership logic.

### Ensemble, Calibration & Delivery
- 11.0 [ ] **Ensemble Diversity & Calibration Guardrails** — evaluate stacking tactics and calibration safety nets.
  - 11.1 [ ] Diversity metrics primer: pairwise Spearman, error correlations, and diversity health checks.
  - 11.2 [ ] Calibration survey: temperature scaling, isotonic fallback, entropy-aware tuning.
  - 11.3 [ ] Post-processing study: clipping policies, range guards, provenance logging.
- 12.0 [ ] **Validation, Drift & Submission QA** — document procedures for leaderboard parity and drift surveillance.
  - 12.1 [ ] Metric replication guide: Spearman plus top-10% recall with correct sign handling.
  - 12.2 [ ] Drift analytics: surprisal KL, entropy delta, charge-shift monitoring frameworks.
  - 12.3 [ ] Submission QA digest: schema validation, SHA logging, manifest composition.

